---
title: "P03 -- Mismatches in Binding and Coreference"
image: /img/project_logos/P3.svg
format:
  html:
    page-layout: full
toc: true
---

::: {.project-hero}

::: {.project-hero-logo}
![](/img/project_logos/P3.svg){alt="P03 project logo"}
:::

::: {.project-hero-text}
### Project description

Project P03 investigates two empirical domains: fake indexicals and other bound pronouns, and unbound pronouns exhibiting covariance. It examines their morphological, syntactic, and semantic properties within a model where syntax mediates between LF and PF by transferring features exhaustively or redundantly. Fake indexicals are analyzed as involving an R operation from syntax to LF, whereas unbound pronouns involve an R operation from syntax to PF. The phenomena thus form mirror images within the CRC’s R/D framework.

The project examines pronoun structure, feature distribution across grammar, mismatches between components, and possible feature sources. It tests two hypotheses: fake indexicals are syntactically bound through the genuine indexical via focus binding, while unbound pronouns are definite noun phrases that undergo ellipsis.

P03 aims to formalize redundancy/deficiency mechanisms and includes a detailed study of fake indexicals in Romance and Slavic languages. Its broad empirical and theoretical scope supports collaboration with most other CRC subprojects.

:::

:::

### Team



```{r, results='asis'}

source('../functions.R')
print_card_members('P03')

```


### Cluster membership

::: {.project-clusters}

[Zero Elements](../clusters/zero-elements.qmd){.project-cluster-badge}

[Syntax and Binding Effects](../clusters/syntax-and-binding-effects.qmd){.project-cluster-badge}

[Semantics and Discourse Effects](../clusters/semantics-and-discourse-effects.qmd){.project-cluster-badge}

:::

### Output

::: {.project-publications}

```{r}
#| output: asis

source("../functions.R", local = knitr::knit_global())

load_publications("P03") %>% 
  print_publications()


```

:::