---
title: "P06 - The (Non-)Deficiency and (Non-)Redundancy of Clitic Pronouns"
image: /img/project_logos/P6.svg
toc: true
---

::: {.project-hero}

::: {.project-hero-logo}
![](/img/project_logos/P6.svg){alt="P06 project logo"}
:::

::: {.project-hero-text}
### Project description

Focusing on clitic doubling (CD), this project investigates the relationship between agreement, clitics, and weak and strong pronouns. It hypothesizes that these forms belong to a single grammatical class but differ in structural size and in the features determining their degree of overt realization. Drawing on Kiparsky’s D-hierarchy, the project models pronominal strength through mechanisms of deficiency and redundancy, including impoverishment and rules of exponence.

It proposes that the feature responsible for repeated realization is [topic], which becomes bleached during grammaticalization. Doubling consequently develops from topic doubling in a particular position into agreement with the highest argument or generalized clitic doubling driven by syntactic locality. Languages therefore exhibit different degrees of doubling—from zero elements and agreement to clitics—depending on grammaticalization and syntactic position. The project examines how this account explains binding, reconstruction, resumption, the Person-Case Constraint, and locality and anti-locality effects associated with clitic pronouns.


:::

:::

### Team



```{r, results='asis'}

source('../functions.R')
print_card_members('P06')

```


### Cluster membership

::: {.project-clusters}

[Romance Data](../clusters/romance.qmd){.project-cluster-badge}

[Clitic Pronouns](../clusters/clitic-pronouns.qmd){.project-cluster-badge}

[Syntax and Binding Effects](../clusters/syntax-and-binding-effects.qmd){.project-cluster-badge}

:::


### Output 


::: {.project-publications}

```{r}
#| output: asis

source("../functions.R", local = knitr::knit_global())

load_publications("P06") %>% 
  print_publications()


```

#### Talks

:::