---
title: "P07 — Deficiency and Redundancy in Iberoromance Pronominal Systems"
image: /img/project_logos/P7.svg
format:
  html:
    page-layout: full
toc: true
---

::: {.project-hero}

::: {.project-hero-logo}
![](/img/project_logos/P7.svg){alt="P07 project logo"}
:::

::: {.project-hero-text}
### Project description

Subproject P07 examines variation in accusative clitic doubling (ACD) and null direct objects (NDOs) within and across Spanish and Portuguese varieties. Although these languages share a substantial inventory of pronominal elements and surface configurations, they differ in striking ways that challenge unified theoretical accounts (Maddox, 2021). Many existing generalizations also require systematic empirical verification.

Building on Di Tullio et al.’s (2019) research on ACD in Rioplatense Spanish, P07 addresses key gaps in the study of null objects across Spanish varieties and clitic doubling in Portuguese. This includes the recently documented ACD system of Mineiro Brazilian Portuguese (Machado Rocha and Ramos, 2016). Through parallel experimental studies, the project will establish a closely comparable dataset for at least four varieties: Rioplatense Spanish, Peninsular Spanish, Mineiro Brazilian Portuguese, and European Portuguese. By investigating minimal contrasts among these systems, P07 aims to determine how redundancy and deficiency operate across closely related but grammatically divergent varieties.


:::

:::

### Team


```{r, results='asis'}

source('../functions.R')
print_card_members('P07')

```



### Cluster membership

::: {.project-clusters}

[Romance Data](../clusters/romance.qmd){.project-cluster-badge}

[Experimental Methods](../clusters/experimental-methods.qmd){.project-cluster-badge}

[Corpus and Annotation](../clusters/corpus-and-annotation.qmd){.project-cluster-badge}

[Clitic Pronouns](../clusters/clitic-pronouns.qmd){.project-cluster-badge}

[Zero Elements](../clusters/zero-elements.qmd){.project-cluster-badge}

[Semantics and Discourse Effects](../clusters/semantics-and-discourse-effects.qmd){.project-cluster-badge}


:::


### Output

::: {.project-publications}

```{r}
#| output: asis

source("../functions.R", local = knitr::knit_global())

load_publications("P07") %>% 
  print_publications()


```

:::