---
title: "P07 — Deficiency and Redundancy in Iberoromance Pronominal Systems"
image: /img/project_logos/P7.svg
format:
  html:
    page-layout: full
toc: true
---

::: {.project-hero}

::: {.project-hero-logo}
![](/img/project_logos/P7.svg){alt="P07 project logo"}
:::

::: {.project-hero-text}
### Project description

This subproject investigates clitic doubling and null objects across Spanish and Portuguese varieties, with a focus on River Plate Spanish and Mineiro Brazilian Portuguese. It examines whether the observed microvariation and gradient acceptability can be explained through the SFB concepts of redundancy and deficiency, including the influence of discourse factors such as familiarity and D-linking.

The project also develops a unified account of these constructions across Iberoromance and evaluates existing proposals, including Maddox’s (2021) Object Agreement Cycle and the Clitic Doubling Parameter proposed by Fischer et al. (2019).
:::

:::

### Team

::: {.project-team-grid}
```{r, results='asis'}

source('../functions.R')
print_card_members('P07')

```

:::

### Cluster membership

::: {.project-clusters}

[Romance Data](../clusters/romance.qmd){.project-cluster-badge}

[Experimental Methods](../clusters/experimental-methods.qmd){.project-cluster-badge}

[Corpus and Annotation](../clusters/corpus-and-annotation.qmd){.project-cluster-badge}

[Clitic Pronouns](../clusters/clitic-pronouns.qmd){.project-cluster-badge}

[Zero Elements](../clusters/zero-elements.qmd){.project-cluster-badge}

[Semantics and Discourse Effects](../clusters/semantics-and-discourse-effects.qmd){.project-cluster-badge}


:::


### Output

::: {.project-publications}

```{r}
#| output: asis

source("../functions.R", local = knitr::knit_global())

load_publications() %>% 
  filter(project=="P07") %>% 
  print_publications()


```

:::