---
title: "P08 -- Fading Reference -- The Pragmaticalization of Pronoun + Verb"
image: /img/project_logos/P8.svg
format:
  html:
    page-layout: full
toc: true
---

::: {.project-hero}

::: {.project-hero-logo}
![](/img/project_logos/P8.svg){alt="P08 project logo"}
:::

::: {.project-hero-text}
### Project description

This project investigates pronoun–verb combinations (prVCs), primarily in spoken Spanish and Italian. It examines their development from content-rich predicates through partially fixed parenthetical constructions to grammaticalized discourse markers. Particular attention is paid to combinations involving verbs of cognition, communication, and perception, and to how their discourse functions depend on pronoun features, verb type and form, additional functional elements, and syntactic position.

The project analyzes how grammatical operations treat pronominal features across morphosyntax, morphophonology, and the syntax–discourse interface. Redundancy (R) may suppress or disregard referential features, while deficiency (D) may reinterpret or enrich them with context-dependent pragmatic features. By tracing these processes, the project models how flexibility at the PF and LF interfaces enables grammatical and pragmatic change and how linguistic, extralinguistic, and frequency-related factors shape the grammatical system. It contributes to the SFB’s questions on grammaticalization and pragmaticalization (Q1), their consequences at the left periphery (Q2), and pronoun feature specifications in prVCs (Q3).

:::

:::

### Team


```{r, results='asis'}

source('../functions.R')
print_card_members('P08')

```



### Cluster membership

::: {.project-clusters}


[Romance Data](../clusters/romance.qmd){.project-cluster-badge}

[Experimental Methods](../clusters/experimental-methods.qmd){.project-cluster-badge}

[Corpus and Annotation](../clusters/corpus-and-annotation.qmd){.project-cluster-badge}

[Clitic Pronouns](../clusters/clitic-pronouns.qmd){.project-cluster-badge}

[Zero Elements](../clusters/zero-elements.qmd){.project-cluster-badge}

[Semantics and Discourse Effects](../clusters/semantics-and-discourse-effects.qmd){.project-cluster-badge}


:::

### Output


::: {.project-publications}

```{r}
#| output: asis

source("../functions.R", local = knitr::knit_global())

load_publications("P08") %>% 
  print_publications()


```

:::