---
title: "P08 -- Fading Reference -- The Pragmaticalization of Pronoun + Verb"
image: /img/project_logos/P8.svg
format:
  html:
    page-layout: full
toc: true
---

::: {.project-hero}

::: {.project-hero-logo}
![](/img/project_logos/P8.svg){alt="P08 project logo"}
:::

::: {.project-hero-text}
### Project description

This project examines pronoun-verb combinations (prVCs), primarily in spoken Spanish and Italian. It focuses on their prototypical occurrence as content-rich predicates, their potentially grammaticalized form as discourse markers, and, most importantly, the varying degrees of fixation in intermediate forms, such as parenthetical ones. The discourse functions of prVCs formed from verbs of cognition, communication, and perception are presented, along with their dependence on pronoun types and their feature characteristics, verb type and form, the presence of other functional elements, and the syntactic positions involved. Basic grammatical operations in morphosyntax and morphophonology, as well as at the semantic-pragmatic interface, appear either to disregard the features present in the pronominal item ( R ) or to reinterpret them at the interface of language language and discourse context as different or additional pragmatic features that were not originally specified as such ( D ). 

This subproject therefore investigates the influence of the feature specification of pronouns with respect to R (suppressing referential features) and D (enriching them with pragmatic features related to the language context) on the development of pronoun-related constructs (prVCs). The subproject contributes to the overarching goals of the Collaborative Research Centre (CRC) by taking a microscopic look at how the flexibility of R and D at the interfaces with phonological features (PF) and language language (LF) can be theoretically modeled to explain the potential for change and the effects of contextual linguistic and extralinguistic factors (including frequency in language use) on the grammatical system. The subproject addresses three main questions of the SFB: Q1 by focusing on grammaticalization/pragmaticalization processes as a strategy for bridging discrepancies between forms and communicative goals, Q2 by investigating the syntactic consequences of these discrepancies at the left periphery, and Q3 by investigating the feature specifications of pronouns in prVCs. 


:::

:::

### Team

::: {.project-team-grid}
```{r, results='asis'}

source('../functions.R')
print_card_members('P08')

```


:::

### Cluster membership

::: {.project-clusters}


[Romance Data](../clusters/romance.qmd){.project-cluster-badge}

[Experimental Methods](../clusters/experimental-methods.qmd){.project-cluster-badge}

[Corpus and Annotation](../clusters/corpus-and-annotation.qmd){.project-cluster-badge}

[Clitic Pronouns](../clusters/clitic-pronouns.qmd){.project-cluster-badge}

[Zero Elements](../clusters/zero-elements.qmd){.project-cluster-badge}

[Semantics and Discourse Effects](../clusters/semantics-and-discourse-effects.qmd){.project-cluster-badge}


:::

### Output


::: {.project-publications}

```{r}
#| output: asis

source("../functions.R", local = knitr::knit_global())

load_publications() %>% 
  filter(project=="P08") %>% 
  print_publications()


```

:::