---
title: "P09 -- Animacy Features and the Flexibility of Pronouns"
image: /img/project_logos/P9.svg
format:
  html:
    page-layout: full
toc: true
---

::: {.project-hero}

::: {.project-hero-logo}
![](/img/project_logos/P9.svg){alt="P09 project logo"}
:::

::: {.project-hero-text}
### Project description

This subproject investigates the mapping between morphosyntactic and semantic features of French and Spanish personal pronouns from the perspective of redundancy and deficiency. Because pronouns have minimal descriptive content, they are highly flexible expressions whose animacy features may vary. French strong pronouns, for example, generally refer to humans but can denote inanimate objects under certain conditions (Heidinger, 2019). Building on the assumption that strong and weak pronouns differ in their animacy specifications, the project examines how R and D manipulate these features to license non-canonical reference.

More broadly, it investigates how redundancy and deficiency allow core grammar to respond to cognitive pressures and the demands of anaphora resolution through flexible pronoun choice. The animacy properties of French and Spanish pronouns, particularly within prepositional phrases, reveal both the scope and limits of this flexibility. Since both languages distinguish strong and weak pronouns but differ in the availability of weak forms in prepositional phrases, they provide an ideal comparative testbed.

:::

:::

### Team


```{r, results='asis'}

source('../functions.R')
print_card_members('P09')

```



### Cluster membership

::: {.project-clusters}


[Romance Data](../clusters/romance.qmd){.project-cluster-badge}

[Experimental Methods](../clusters/experimental-methods.qmd){.project-cluster-badge}

[Clitic Pronouns](../clusters/clitic-pronouns.qmd){.project-cluster-badge}

[Zero Elements](../clusters/zero-elements.qmd){.project-cluster-badge}

[Semantics and Discourse Effects](../clusters/semantics-and-discourse-effects.qmd){.project-cluster-badge}

:::


### Output

::: {.project-publications}

```{r}
#| output: asis

source("../functions.R", local = knitr::knit_global())

load_publications("P09") %>% 
  print_publications()


```

:::